### 2021-01-26 doc/manuscript/Dow_manuscript_Nature.Rmd
a few updates

@@

schematic_summary_caption <- "Figure 1 | Summary of tree growth changes under warmer spring temperatures at two temperate forests and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous). (a) Schematic illustrating parameters of interest and summarizing how each responds to warmer maximum temperatures during a 'critical temperature window', defined as that with the strongest control over DOY25; (b) Variable definitions and summary responses to warmer temperatures, where up and down arrows indicate increases and decreases, respectively, 'n.s.' indicates no signficant correlation, and 'mixed' indicates a mix of signficant and non-signficant correlations, often in different directions."

@@

Mixed effects models were used to test the response of growth phenology variables ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, $DOY_{g_max}}$, $g_{max}$, and $\Delta DBH$) to fixed effects of xylem porosity and mean temperature ($T_{max}$, $T_{min}$) during the critical temperature window selected by *climwin*, along with random effects of species and tree. 
We ran separate models for each species group at each site, and for the response of all growth phenology variables to $T_{max}$ and $T_{min}$. 
Models were run using the LME4 package in R [@bates_fitting_2015].

>>>>

Justin Maxwell

@@

schematic_summary_caption <- "Figure 1 | Summary of tree growth changes under warmer spring temperatures. (a) Schematic illustrating parameters of interest and summarizing how each responds to warmer maximum temperatures during a 'critical temperature window', defined as that with the strongest control over $DOY_{25}$; (b) Variable definitions and summary responses to warmer spring temperatures at two temperate forests and for two groups of broadleaf deciduous species (RP=ring porous; DP=diffuse porous), where up and down arrows indicate increases and decreases, respectively, 'n.s.' indicates no signficant correlation, and 'mixed' indicates a mix of signficant and non-signficant correlations, often in different directions."

@@

Mixed effects models were used to test the response of growth phenology variables ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, $DOY_{g_max}$, $g_{max}$, and $\Delta DBH$) to fixed effects of xylem porosity and mean temperature ($T_{max}$, $T_{min}$) during the critical temperature window selected by *climwin*, along with random effects of species and tree. 
We ran separate models for each species group at each site, and for the response of all growth phenology variables to $T_{max}$ and $T_{min}$. 
Models were run using the LME4 package in R [@bates_fitting_2015].
